Manuscript

### 2021-08-19 Manuscript/Manuscript_Results.Rmd
update

By evaluating how often the BART algorithm decided to use a term for classification, it is possible to list a subset of the variables most relevant for the classification of the documents: `r var_importance`. In parenthesis, it is reported the part of the record in which the term was used, while the numeric values indicate respectively the rate of posterior trees (over 10000 trees) in which a term was used, and the number of standard errors of the association between a term and the probability of a positive match according to a simple logistic linear model (see methods). The "&" indicates that two terms are present together in a document but not close to each other.\
The engine was able to pick up the central concept of the research (i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections) and even one of the authors of the current study (Donker T.) or the region of interest ("Orange County") of another research group active on the topic. It is interesting to see that some terms were considered highly relevant (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model, their effect would be hardly significant (statistic: -1.21 se), and this highlight the extra predictive power brought by a highly non-linear model.\
A more extensive set of terms is presented in Table 1 of Supplemental Material S2.

@@

To evaluate the theoretical performance of the engine on the full datasets (i.e., session1 and session2 data), a Bayesian logistic model was trained on each session dataset to predict the label of the records from the probability estimated by the engine (see methods for details). The performance of such simple models is quite high (Bayesian R2: `r Performance$s1$mod_r2 %>% format_interval(percent = TRUE)` for session 1 and `r Performance$s2$mod_r2 %>% format_interval(percent = TRUE)` for session 2) and the median of their cumulative predictive distribution matches quite well the actual number of cumulative positive records found. The predicted cumulative number of positive matches was used to evaluate the performance in the non-reviewed records (Table 3).\

Figure 1 shows the actual and predicted (from the logistic model) cumulative number of positive matches, ordered by the initial simple ordering query. As confirmed by the high efficiency values reported in Table 3, it is striking how many more records would need to be evaluated manually to find all positive matches without using a smart search tool. Our engine was able to find matches even close to the end of the heuristically ordered list of records.
Specifically, in session 1 we observe an expected total number of positives of `r Performance$s1$pred_positives %>% format_interval()` for an estimated sensitivity of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)` and efficiency of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)`.\
In session 2 we observed a drop in the expected sensitivity, especially in the lower margin (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`), due to the fact that as the number of records grows very large, even a small probability can translate, in the worst scenario, into a relevant number of predicted positive matches (`r Performance$s2$pred_positives %>% max()` in this case). To ascertain that no evident positives were missed, we evaluated 100 more records between the unreviewed ones with the highest median predicted probability produced by the engine and found no actual positive matches.

>>>>

By evaluating how often the BART algorithm decided to use a term for classification, it is possible to list a subset of the variables most relevant for the classification of the documents: `r var_importance`. In parenthesis, it is reported the part of the record in which the term was used, while the numeric values indicate respectively the rate of posterior trees (over 10000 trees) in which a term was used, and the number of standard errors of the association between a term and the probability of a positive match according to a simple logistic linear model (see methods). The "&" indicates that two terms are present together in a document but not close to each other.\
The engine was able to pick up the central concept of the research (i.e., "patient transport" or "transfer" through a "network" of "facility"ies that facilitates the "spread" of infections) and even one of the authors of the current study (Donker T.) or the region of interest ("Orange County") of another research group active on the topic. It is interesting to see that some terms were considered highly relevant (e.g., "Worker" in 6th position out of more than 3800 terms considered) although in a simpler linear model, their effect would be hardly significant (statistic: -1.21 s.e.), and this highlight the extra predictive power brought by a highly non-linear model.\
A more extensive set of terms is presented in Table 1 of Supplemental Material S2.

@@

To evaluate the theoretical performance of the engine on the full datasets (i.e., session 1 and session 2 data), a Bayesian logistic model was trained on each session dataset to predict the label of the records from the probability estimated by the engine (see methods for details). The performance of such simple models is quite high (Bayesian R2: `r Performance$s1$mod_r2 %>% format_interval(percent = TRUE)` for session 1 and `r Performance$s2$mod_r2 %>% format_interval(percent = TRUE)` for session 2) and the median of their cumulative predictive distribution matches quite well the actual number of cumulative positive records found. The predicted cumulative number of positive matches was used to evaluate the performance in the non-reviewed records (Table 3).\

Figure 1 shows the actual and predicted (from the logistic model) cumulative number of positive matches, ordered by the initial simple ordering query. As confirmed by the high efficiency values reported in Table 3, it is striking how many more records would need to be evaluated manually to find all positive matches without using a smart search tool. The engine was able to find matches even close to the end of the heuristically ordered list of records.
Specifically, in session 1 we observe an expected total number of positives of `r Performance$s1$pred_positives %>% format_interval()` for an estimated sensitivity of `r Performance$s1$sensitivity %>% format_interval(percent = TRUE)` and efficiency of `r Performance$s1$efficiency %>% format_interval(percent = TRUE)`.\
In session 2 we observed a drop in the expected sensitivity, especially in the lower margin (`r Performance$s2$sensitivity %>% format_interval(percent = TRUE)`), due to the fact that as the number of records grows very large, even a small probability can translate, in the worst scenario, into a relevant number of predicted positive matches (`r Performance$s2$pred_positives %>% max()` in this case). To ascertain that no evident positives were missed, we evaluated 100 more records between the unreviewed ones with the highest median predicted probability produced by the engine and found no actual positive matches.
